Constructing Biological Regulatory Networks from Process Hitting models \\\rewrite{Or possibly: “Complementarity between PH, IG and Thomas modeling”}

### 2013-06-14 parts/intro.tex
several TODOs

\section{Introduction}\label{sec:intro}
As regulatory phenomena play a crucial role in biological systems, they need to be studied accurately.
Biological Regulatory Networks (BRNs) consist in sets of either positive or negative mutual effects between the components.
With the purpose of analyzing these systems, they are often modeled as graphs which make it possible to determine the possible evolutions of all the interacting components of the system.
Indeed, besides continuous models of physicists, often designed through systems of ordinary
differential equations, a discrete modeling approach was initiated by René Thomas in 1973
\cite{Thomas73}.

>>>>

\section{Introduction}\label{sec:intro}

\rewrite{Include Olivier's additions}

\rewrite{Emphasize on the results on IGs (multistationarity, cyclic attractors) and parameters (?) and its complementarity with PH (reachability, fixed points)}

\rewrite{Idea: IG abstracts PH abstracts BRN}

As regulatory phenomena play a crucial role in biological systems, they need to be studied accurately.
Biological Regulatory Networks (BRNs) consist in sets of either positive or negative mutual effects between the components.
With the purpose of analyzing these systems, they are often modeled as graphs which make it possible to determine the possible evolutions of all the interacting components of the system.
Indeed, besides continuous models of physicists, often designed through systems of ordinary
differential equations, a discrete modeling approach was initiated by René Thomas in 1973
\cite{Thomas73}.
